%\documentclass[sigconf,anonymous]{acmart}
\documentclass[acmlarge,screen]{acmart}

\input{setup/packages}
\input{setup/macros}
\input{setup/alg}


\begin{document}

\title{Demystifying Stablecoins}
\subtitle{Cryptography meets monetary policy}

\author{Jeremy Clark}
\affiliation{\institution{Concordia University}}
\authornote{Authors listed alphabetically. D. Demirag and S. Moosavi should be considered equal first authors.}

\author{Didem Demirag}
\affiliation{\institution{Concordia University}}

\author{Seyedehmahsa Moosavi}
\affiliation{\institution{Concordia University}}

\begin{abstract} Stablecoins promise the functionality of Bitcoin without the rollercoaster ride of its exchange rate. But can this new breed of cryptocurrency really outsmart decades of central bank policy with algorithms and smart contracts?\end{abstract}

\maketitle

%==========================================%

\input{sections/stablecoin}

%==========================================%

\bibliographystyle{ACM-Reference-Format}
\bibliography{bib/stablecoinRef, bib/pulp}

%==========================================%

% \input{sections/appendix}

\begin{Sidebar*}[h!]
\begin{framed}
\begin{flushleft}
\textbf{Related Articles on ACM Queue.} \newline

Bitcoin’s Academic Pedigree \\
by Arvind Narayanan and Jeremy Clark \\
https://queue.acm.org/detail.cfm?id=3136559 \newline

Blockchain Technology: What Is It Good for? \\ 
by Scott Ruoti, Ben Kaiser, Arkady Yerukhimovich, Jeremy Clark, and Robert Cunningham \\
https://queue.acm.org/detail.cfm?id=3376896 \newline

A Hitchhiker’s Guide to the Blockchain Universe\\
by Jim Waldo \\
https://queue.acm.org/detail.cfm?id=3305265
\end{flushleft}
\end{framed}
\end{Sidebar*}

\begin{Sidebar*}[h!]
\begin{framed}
\begin{flushleft}
\textbf{Authors.} \newline

\textbf{Jeremy Clark} is an associate professor at the Concordia Institute for Information Systems Engineering in Montreal, Canada, where he holds the NSERC/RCGT/Catallaxy Industrial Research Chair in Blockchain Technologies. He collaborates regularly with government agencies on voting and blockchain technologies. \newline

\textbf{Didem Demirag} is a PhD student at the Concordia Institute for Information Systems Engineering in Montreal. \ldots \newline

\textbf{Seyedehmahsa Moosavi} is a Ph.D. student at the Concordia Institute for Information Systems Engineering in Montreal, Canada. She previously worked as a research intern at the Autorité des Marchés Financiers, Québec, and now focuses on understanding the future of financial technologies (FinTech) using blockchains. \newline

\end{flushleft}
\end{framed}
\end{Sidebar*}



%==========================================%

\end{document}
